A continuous urbanization index to assess phylogenetic adaptations in urban bird living

### 2018-05-04 ms.Rmd
more formatting stuff

# Supplementary figures
```{r Figure S1, echo=FALSE, fig.cap="A correlation plot for the continuous variables used in the modelling procedures."}
knitr::include_graphics("figures/corrplot_of_continuous_variables.pdf")
```

>>>>

# Supplementary figures
\newcommand{\beginsupplement}{%
        \setcounter{table}{0}
        \renewcommand{\thetable}{S\arabic{table}}%
        \setcounter{figure}{0}
        \renewcommand{\thefigure}{S\arabic{figure}}%
     }
     \beginsupplement

```{r Figure S1, echo=FALSE, fig.cap="A correlation plot for the continuous variables used in the modelling procedures."}
knitr::include_graphics("figures/corrplot_of_continuous_variables.pdf")
```
